doe-pkgs-analysis

### 2021-09-12 analysis/doe-pkgs-analysis.Rmd
Compare interconnection with other CRAN Task View.

```{r}
# shinyApp(
#   ui = fluidPage(
#     selectInput("first_aut", "Choose the author:",
#                     choices = levels(pkg_nodes_1aut$first_aut)),
#       mainPanel(plotOutput(outputId = "net"))
#     ),
#   
#   server = function(input, output){
#     
#     dat <- reactive({
#       if (input$first_aut == "Ulrike Groemping"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Ulrike Groemping", "Ulrike Groemping", "Other")))
#       }
#       
#       if (input$first_aut == "John Lawson"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "John Lawson", "John Lawson", "Other")))
#       }
#       
#       if (input$first_aut == "Robert B. Gramacy"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Robert B. Gramacy", "Robert B. Gramacy", "Other")))
#       }
#       
#       if (input$first_aut == "Delphine Dupuy"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Delphine Dupuy", "Delphine Dupuy", "Other")))
#       }
#       
#       if (input$first_aut == "Ernesto Barrios"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Ernesto Barrios", "Ernesto Barrios", "Other")))
#       }
#       
#       if (input$first_aut == "Kevin Wright"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Kevin Wright", "Kevin Wright", "Other")))
#       }
#       
#        if (input$first_aut == "Peng Liu"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Peng Liu", "Peng Liu", "Other")))
#        }
#       
#       if (input$first_aut == "Shwetank Lall"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "Shwetank Lall", "Shwetank Lall", "Other")))
#       }
#       
#       if (input$first_aut == "other"){
#         aut <- pkg_nodes_1aut %>%
#           mutate(author = as.factor(ifelse(first_aut == "other", "Other authors", "Other with > 1 packages")))
#       }
#       
#       graph_from_data_frame(d = pkg_edges, vertices = aut, directed = TRUE) %>%
#         as_tbl_graph() %>% activate(edges)
#     })
#     
#     
# 
#     output$net <- renderPlot(
#       ggraph(dat, layout = "stress") +
#         geom_edge_link(aes(color = type),
#                        arrow = arrow(length = unit(2, 'mm')),
#                        end_cap = circle(1, 'mm')) +
#         geom_node_point(aes(color = author), size = 3) +
#         geom_node_text(aes(label = name), repel = TRUE, size = 3.5) +
#         scale_color_manual(values = c("black", "#6C3483")) +
#         theme_graph()
#     )
#   },
#   
#   options = list(height = 1500,
#                  width = 1500)
#   
# )
```

>>>>

# Comparison to other CRAN TASK VIEW

## Survey

```{r}
list_pkg_survey <- ctv:::.get_pkgs_from_ctv_or_repos("OfficialStatistics", 
                                                repos = "http://cran.rstudio.com/")[[1]]
url <- "http://cran.rstudio.com/web/packages/packages.rds"
db <- readRDS(url(url)) %>% 
  as.data.frame()
survey_pkg <- db %>%
  filter(Package %in% list_pkg_survey) %>%
  select(Package, Depends, Imports, Suggests)

get_pkg_survey <- function(var){
  # select only the package name and depends/imports/suggests
  tmp_df <- survey_pkg %>%
    select(Package, var) %>%
    # separate every depends/imports/suggests
    cSplit(var, sep = " ,")

  df <- tmp_df %>%
    pivot_longer(c(2:ncol(tmp_df)), names_to = "type", values_to = "pkg") %>%
    filter(!is.na(pkg)) %>%
    # check if the depends/imports/suggests is also a DoE package (is in list_pkg)
    mutate(survey_pkg_related = ifelse(pkg %in% list_pkg_survey, "yes", "no")) %>%
    # filter only package whose depends/imports/suggests is a DoE
    filter(survey_pkg_related == "yes") %>%
    # tidy the data to only have the type: depends/imports/suggests
    cSplit("type", sep = "_") %>%
    select(-type_2) %>%
    rename(type = type_1)

  return(df)
}

survey_depends <- get_pkg_survey("Depends")
survey_imports <- get_pkg_survey("Imports")
survey_suggests <- get_pkg_survey("Suggests")

pkg_edges_survey <- rbind(survey_depends, survey_imports, survey_suggests)

survey_from <- pkg_edges_survey %>%
  distinct(Package)

# extract unique package that being depends/imports/suggests
survey_to <- pkg_edges_survey %>%
  distinct(pkg)

# create nodes from the two previous dataframe
pkg_nodes_survey <- full_join(survey_from, survey_to, by = c("Package" = "pkg"))
```

## Timeseries

```{r}
list_pkg_ts <- ctv:::.get_pkgs_from_ctv_or_repos("TimeSeries", 
                                                repos = "http://cran.rstudio.com/")[[1]]

ts_pkg <- db %>%
  filter(Package %in% list_pkg_ts) %>%
  select(Package, Depends, Imports, Suggests)

get_pkg_ts <- function(var){
  # select only the package name and depends/imports/suggests
  tmp_df <- ts_pkg %>%
    select(Package, var) %>%
    # separate every depends/imports/suggests
    cSplit(var, sep = " ,")

  df <- tmp_df %>%
    pivot_longer(c(2:ncol(tmp_df)), names_to = "type", values_to = "pkg") %>%
    filter(!is.na(pkg)) %>%
    # check if the depends/imports/suggests is also a DoE package (is in list_pkg)
    mutate(survey_pkg_related = ifelse(pkg %in% list_pkg_ts, "yes", "no")) %>%
    # filter only package whose depends/imports/suggests is a DoE
    filter(survey_pkg_related == "yes") %>%
    # tidy the data to only have the type: depends/imports/suggests
    cSplit("type", sep = "_") %>%
    select(-type_2) %>%
    rename(type = type_1)

  return(df)
}

ts_depends <- get_pkg_ts("Depends")
ts_imports <- get_pkg_ts("Imports")
ts_suggests <- get_pkg_ts("Suggests")

pkg_edges_ts <- rbind(ts_depends, ts_imports, ts_suggests)

ts_from <- pkg_edges_ts %>%
  distinct(Package)

# extract unique package that being depends/imports/suggests
ts_to <- pkg_edges_ts %>%
  distinct(pkg)

# create nodes from the two previous dataframe
pkg_nodes_ts <- full_join(ts_from, ts_to, by = c("Package" = "pkg"))
```
